Covid-19 A Spatio-Temporal Investigation.

### 2021-01-03 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 With the whole world being affected by the pandemic, it's a matter of great importance that studies about the Spatio-temporal aspects of the Covid-19 pandemic should be conducted, by evaluating the number of cases and deaths in different countries accordingly to time in the year 2020 we can contribute with methods to analyze Spatio-temporal behavior in future disease outbreaks.

 Ao traçar um perfil sobre o comportamento espaço-temporal da Covid-19, estudos como esse poderão ser analisados para lidar com possíveis pandemias causadas por vírus que apresentem características similares a Sars-CoV-2.

>>>>

 With the whole world being affected by the pandemic, it's a matter of great importance that studies about the Spatio-temporal aspects of the Covid-19 pandemic should be conducted, by evaluating the number of cases and deaths in different countries accordingly to time in the year 2020, we can contribute with methods to analyze Spatio-temporal behavior in future disease outbreaks.
